This is an example of article title

### 2025-10-28 paper/paper.tex
Started with meta Lie groups.

\subsubsection{Product Lie groups}
\subsubsection{Power Lie groups}
\subsubsection{Semidirect product Lie groups}

>>>>

\subsubsection{Product Lie group}

Given two Lie groups \(\mathcal{G} = (\mathcal M, \ast) \) and \(\mathcal{H} = (\mathcal N, \diamond)\), their (direct) product \(\mathcal{G} \times \mathcal{H}\) is again a Lie group \((\mathcal{M} \times \mathcal{N}, \cdot)\) with group operation defined component-wise, i.e.
\begin{equation*}
    (g_1, h_1) \cdot (g_2, h_2) = (g_1 \ast g_2, h_1 \diamond h_2)
\end{equation*}
for \(g_1, g_2 \in \mathcal{G}\) and \(h_1, h_2 \in \mathcal{H}\).
Since $\times$ is a binary operator in Julia, given two Lie Groups \verb|G,H|, their product Lie group can be constructed via \verb|G|\,$\times$\,\verb|H|.
The same applies for more than two groups, i.e. you can construct arbitrary long product Lie groups \verb|G1|\,$\times$\,\verb|G2|\,$\times$\,\verb|G3|\,$\times$\,\ldots.

As for the representation of points and tangent vectors, the default representation requires to load \verb|RecursiveArrayTools.jl|\footnote{see \href{https://docs.sciml.ai/RecursiveArrayTools/stable/}{docs.sciml.ai/RecursiveArrayTools/stable/}}.

If you want to construct nested Products of Lie groups, e.g.\ \((\mathcal G_1 \times \mathcal G_2) \times \mathcal G_3\), the binary operator would not work, since it automatically flattens the input; use \verb|ProductLieGroup(ProductLieGroup(G1, G2), G3)| can be used instead.

\subsubsection{Power Lie groups}
Though mathematically the case of a product Lie Group, where $G=H$ is also (just) a product, computationally we can benefit from the special structure. Therefore the \verb|Powermanifold(G, n1, n2, ...)| is provided to construct the \(n_1 \times n_2 \times \ldots\)-fold Cartesian product of the Lie group \(G\) with itself.
As a shortcut, you can use \verb|G^n| to construct the \(n\)-fold Cartesian product of the Lie group \(G\) with itself.

Note that inheriting from the power manifold, there are two different data types to represent data, per default a single large array, or a

\subsubsection{Semidirect product Lie groups}
